---
title: "Class 12: Structural Bioinformatics pt.1"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## GitHub Documents

## From Template -> Github document

## PDB Statistics 

Here we inspect the types of structures in the main database for 3D biomolecular data - the PDB

> Q1: Download a CSV file from the PDB site (accessible from “Analyze” -> “PDB Statistics” >
“by Experimental Method and Molecular Type”. Move this CSV file into your RStudio project
and determine the percentage of structures solved by X-Ray and Electron Microscopy. 

```{r}
#read in file

#Calculate the percentage of structures solved by x-ray and EM.

stats <- read.csv("Data Export Summary.csv", row.names = 1)
ans <- stats$Total /sum(stats$Total) * 100
names(ans) <- rownames(stats)
round(ans, 2)

```


> Q2: Also can you determine what proportion of structures are protein? Aim to have a rendered GitHub document with working code that yields your answers.

```{r}
round(sum(stats$Proteins) / sum(stats$Total) * 100, 2)
```


> Q3: Type HIV in the PDB website search box on the home page and determine how many
HIV-1 protease structures are in the current PDB?









































































